# Basic EDA for case study B
## Telco


```{r, echo=FALSE, include=FALSE}
library(tidyverse)
library(readxl)
library(ggpubr)
library(corrr)
library(GGally)
```



```{r, echo=FALSE, include=FALSE}
telco <- read_excel("Btelco.xls")
```


```{r}
summary(telco)
telco[1,]
attach(telco)
str(telco)
```

Cols:       
1-2: basic customer info        
3-19: call data (duration)      
20-24: tariff schemes (cost)        

All variables are numeric.

```{r, echo=FALSE, include=FALSE}
telco[!complete.cases(telco),]
```
We have no NAs.

### Overall

```{r}
pairs_tot <- ggpairs(telco, aes(alpha = 0.4))
pairs_tot
```

Can't see anything!

```{r}
pairs1_2 <- ggpairs(telco[, 1:2], aes(alpha = 0.4))
pairs1_2
```

`Age` is not so special. No correlation. `L_O_S` is bimodal, 2 groups ?

```{r}
#It's quite slow..
pairs3_19 <- ggpairs(telco[, 3:19], aes(alpha = 0.4))
pairs3_19
```

`Nat_call_cost_Sum`, `National_mins`, `All_calls_mins` -> multinomial distrib?

`Peak_mins_Sum` together with `Nat_call_cost_Sum` -> 2 clusters

```{r}
pairs20_24 <- ggpairs(telco[, 20:24], aes(alpha = 0.4))
pairs20_24
```

All variables multinomial, tariffs grouping?

Let's explore a subset of the interesting variables:

```{r}
subset <- telco[c(1:2, 5, 11, 16, 18, 20:24)]
pairs_sub <- ggpairs(subset, aes(alpha = 0.4))
pairs_sub
```


### Basic customer info
```{r}
summary(telco[, 1:2])
boxplot(telco[, 1:2])

ggplot(data=telco) + 
    geom_histogram(mapping = aes(x = Age), binwidth = 1)

ggplot(data=telco) + 
    geom_histogram(mapping = aes(x = L_O_S), binwidth = .8)

#The outlier
telco[which(telco$Age==82),]
```

Just one outlier for `Age`. 

```{r, echo=FALSE}
telco_cor <- telco %>%
    correlate() %>%
    rearrange(method = "MDS", absolute = FALSE) %>%
    shave() 
telco_cor

telco_cor_plot <- telco_cor %>%
    rplot(shape = 19, colors = c("red", "green")) +
    theme(axis.text.x = element_text(angle = 90))
telco_cor_plot
```




Questions:
- does the client know what "kind of groups" he wants?

