---
title: "EDA case B"
output:
  pdf_document: default
  html_document: default
---

# Basic EDA for case study B
## Telco

```{r include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r, echo=FALSE, include=FALSE}
library(tidyverse)
library(readxl)
library(ggpubr)
library(corrr)
library(GGally)
library(dplyr)
library(gridExtra)
```

Updated EDA with Vivian's model
```{r}
telco <- read.csv("6_groups_telco.csv")

telco$group <- as.factor(telco$group)
str(telco)
```

```{r}
# Sanity check
summary(telco)
telco[1,]
telco[, ncol(telco)]
str(telco)
```

Cols:       
1-2: basic customer info        
3-19: call data (duration)      
20-24: tariff schemes (cost)        

All variables are numeric.

```{r, echo=FALSE, include=FALSE}
telco[!complete.cases(telco),]
```
We have no NAs.

### Overall

```{r}
#pairs_tot <- ggpairs(telco, aes(color = group, alpha = 0.4))
#pairs_tot
```

```{r}
#pairs1_2 <- ggpairs(telco[, c(1:2, 25)], aes(color = group, alpha = 0.4))
#pairs1_2
#ggsave(gsub(" ", "", paste("figures/pairs/gp_pairs1_2.png")), width=10, height=6, units="in")
```


```{r}
#It's quite slow..
#pairs3_19 <- ggpairs(telco[, c(3:19, 25)], aes(color = group, alpha = 0.4))
#pairs3_19
#ggsave(gsub(" ", "", paste("figures/pairs/gp_pairs3_19.png")), width=30, height=18, units="in")
```

`Nat_call_cost_Sum`, `National_mins`, `All_calls_mins` -> multinomial distrib?

```{r}
# pairs20_24 <- ggpairs(telco[, 20:25], aes(color = group, alpha = 0.4))
# pairs20_24
# ggsave(gsub(" ", "", paste("figures/pairs/gp_pairs20_24.png")), width=6.5, height=4.5, units="in")
```

--> No more subset
```{r}
ggplot(data=stack(telco), aes(ind, values)) + geom_boxplot() + theme_minimal() +
  theme(axis.text.x = element_text(angle=90)) +  
  xlab("variables") + ggsave("figures/bxplt_all.png", width=7, height=4)
```


### Misc

A few subsets to use.

```{r}
sub1_2 <- telco[, c(1:2, 25)]
sub3_19 <- telco[, c(3:19, 25)]
sub20_24 <- telco[, c(20:25)]

# Per groups
sub1 <- telco[which(telco$group==1),]
sub2 <- telco[which(telco$group==2),]
sub3 <- telco[which(telco$group==3),]
sub4 <- telco[which(telco$group==4),]
sub5 <- telco[which(telco$group==5),]
sub6 <- telco[which(telco$group==6),]


## No more submodel

# From the model (only the interesting variables)
#names <- as.vector(colnames(data_norm))
#names <- c("group", "Peak_calls_Sum", "Peak_mins_Sum", "OffPeak_calls_Sum", "OffPeak_mins_Sum", "International_mins_Sum", "Nat_call_cost_Sum", "National_calls", "National_mins", "All_calls_mins", "Mins_charge", "call_cost_per_min", "actual.call.cost", "Total_call_cost", "Total_Cost", "average_cost_min")
#names[12] <- "actual.call.cost"
#submodel <- telco %>% select(all_of(names))
```

## Groups comparison

```{r}
# delete "group" col to avoid errors 
cols_submodel <- colnames(telco)[-25]
```

### General
```{r}
ggplot(data = telco, aes(x = group, fill = group)) + geom_bar() +
  scale_fill_viridis_d(begin = 0.2, end = 0.85) + theme_minimal() + 
  ggsave("figures/barplot_groups.png")
```


### Histograms

```{r}
hist_col <- function (data, column) {
    if(class(column) == "factor"){
      stop("Factor")
    }
  ggplot(data = data, aes_string(x = column, color = data$group)) +
      geom_freqpoly(binwidth = 30) +
      xlab(column) + theme_minimal() + scale_fill_viridis_d(begin = 0.2, end = 0.85) +
      labs(title=paste0(column)) +
    ggsave(gsub(" ", "", paste("figures/hist/6_hist_", column, ".png")))
}
```

```{r}
histograms <- lapply(cols_submodel, hist_col, data = telco)
histograms
```


### Boxplots

```{r}
# Generate a boxplot for each column of the data for each group
box_col <- function (data, column) {
  ggplot(data = data, aes_string(x = column, y = data$group)) +
    geom_boxplot(mapping = aes(color = group)) + xlab(column) + ylab("groups") +
    scale_fill_viridis_d(begin = 0.2, end = 0.85) + theme_minimal() + 
    labs(title = paste0(column)) + scale_y_discrete(limits = rev) + 
    ggsave(gsub(" ", "", paste(
      "figures/boxplots/6_bxplt_", column, ".png"
    )), width = 3, height = 2)
}
```

```{r}
boxplots <- lapply(cols_submodel, box_col, data = telco)
boxplots
```

```{r}
# Generate a faceted figure of dimensions w*h, with number of columns and rows.
# Suited for the report
fig.gen <-
  function(cols,
           name,
           w = 6,
           h = 3,
           ncol = 3,
           nrow = 1,
           norm = FALSE) {
    
    subcols <- append(cols, "group", 0)
    fig <- telco %>% select(all_of(subcols))
    
    if (norm) {
      fig[, 2:length(subcols)] <- apply(fig[, 2:length(subcols)], 2, FUN = scale)
      scale_x = "fixed"
    }
    else{
      scale_x = "free_x"
    }
    
    
    fig.long <- fig %>%
      gather(key, value, subcols[-1])
    
    ggplot(data = fig.long, aes(x = value, y = group, fill = group)) +
      geom_boxplot() + facet_wrap(~ key,
                                  scales = scale_x,
                                  ncol = ncol,
                                  nrow = nrow) +
      scale_fill_viridis_d(begin = 0.2, end = 0.85) +
      scale_y_discrete(limits = rev) + theme_minimal() +
      ggsave(
        paste0("figures/boxplots/6_bxplt_", name, ".png"),
        width = w,
        height = h
      )
  }
```

```{r}
fig.basic <- fig.gen(c("Age", "L_O_S"), "fig.basic", ncol=2)
fig.basic
```


```{r}
fig1 <-
  fig.gen(
    cols = c("All_calls_mins", "OffPeak_mins_Sum", "Peak_mins_Sum"),
    name = "fig1"
  )

fig1.2 <-
  fig.gen(
    c(
      "OffPeak_mins_Sum",
      "Peak_mins_Sum",
      "Weekend_mins_Sum", "AvePeak", "AveOffPeak", "AveWeekend"
    ),
    "fig1.2",
    nrow=2,
    h=6,
    w=7
  )
fig1.2

fig1.3 <- fig.gen(c("AvePeak", "AveOffPeak", "AveWeekend"), "fig1.3")
fig1.3
```

```{r}
fig2 <- fig.gen(c("OffPeak_calls_Sum", "Peak_calls_Sum"), "fig2", w=5, h=3)

fig2.1 <- fig.gen(c("OffPeak_calls_Sum", "Peak_calls_Sum", "Dropped_Calls", "Weekend_calls_Sum"), "fig2", ncol=4, w=7)
fig2.1
```

```{r}
fig3 <-
  fig.gen(c("National_mins", "International_mins_Sum", "National_calls", "AveNational", "All_calls_mins"),
          "fig3", w=8, ncol=5)
fig3

```

```{r}
fig4 <- fig.gen(c(
  "Nat_call_cost_Sum",
  "actual.call.cost",
  "Mins_charge",
  "call_cost_per_min"
), "fig4", w=7, h=3, ncol=4)
fig4
```

```{r}
fig5 <- fig.gen(c("average_cost_min", "Total_Cost", "Total_call_cost"), "fig5")
fig5
```



```{r}
telco.scaled <- telco
telco.scaled[, 1:24] <- apply(telco.scaled[, 1:24], 2, FUN=scale)

summ.fig.longA <- telco.scaled[c(1:12, 25)] %>%
  gather(key,
         value,
        names(telco[1:12])[names(telco[1:12]) != "group"])

summ.fig.longB <- telco.scaled %>%
  gather(key,
         value,
        names(telco[13:24])[names(telco[13:24]) != "group"])

ggplot(data = summ.fig.longA, aes(x = value, y = key, fill = group)) +
  geom_boxplot() + scale_fill_viridis_d(begin = 0.2, end = 0.85) + 
  facet_wrap( ~ group, ncol=6) + scale_y_discrete(limits = rev) +
  theme_minimal() +
  ggsave(gsub(" ", "", paste("figures/boxplots/6_bxplt_summfigA.png")), width = 10, height = 6)

ggplot(data = summ.fig.longB, aes(x = value, y = key, fill = group)) +
  geom_boxplot() + scale_fill_viridis_d(begin = 0.2, end = 0.85) +
  facet_wrap( ~ group, ncol=6) + scale_y_discrete(limits = rev) +
  theme_minimal() +
  ggsave(gsub(" ", "", paste("figures/boxplots/6_bxplt_summfigB.png")), width = 10, height = 6)

```


## Groupwise EDA

Perform a small EDA for each group to see if we can extract some obvious features.

Let's recall the overall summary:
```{r}
# Color per group
gp_cols <- c("#F8766D", "#B79F00", "#00BA38", "#00BFC4")
```

```{r}
# Compare the median of the subgroup
# wrt to base
gen_compare_med <- function(summ, base){
  med1 <- summ[[3]]
  med2 <- base[[3]]
  base_1qr <- base[[2]]
  base_3qr <- base[[5]]

  #print(paste("med1", med1))
  #print(paste("med2", med2))
  
  if(med1 > base_3qr){
    print("Bigger than 3rd base quartile")
  }
  else if(med1 >= med2){
    print("Bigger than base median")
  }
  else if(med1 <= med2){
    if(med1 < base_1qr){
      print("Smaller than 1st base quartile")
    }
    else{
      print("Smaller than base median") 
    }
  }
}
```

```{r}
# Dynamically create 2 boxplots to compare
gen_compare_plot <- function(subgroup, col, summary=FALSE){
  group_nb <- subgroup$group[1]
  ymin <- min(telco[, col]) - .1 * min(telco[, col])
  ymax <- 1.1 * max(telco[, col])
  
  b1 <- ggplot(data=subgroup, aes_string(y = subgroup[, col], x=subgroup$group, fill=subgroup$group)) + ylim(c(ymin, ymax)) + geom_boxplot(width=0.4)
  
  b2 <- ggplot(data=telco, aes_string(y = telco[, col], x = group_nb)) + ylim(c(ymin, ymax)) + geom_boxplot(width=0.4)
  
  grid.arrange(b1, b2, ncol=2, top=paste("group", group_nb, col))
  g <- arrangeGrob(b1, b2, ncol=2, top=paste("group", group_nb, col))
  ggsave(gsub(" ", "", paste("figures/boxplots/compare/", group_nb, "_", col, ".png")), g, width=10, height=6.3, units="in")
  
  # Compare the medians
  med_compar <- gen_compare_med(summary(subgroup[, col]), summary(telco[, col]))
  
  return(med_compar)
}

```

### 1.

For each variable, check the boxplot (`figures/boxplots`). Let's focus on the model variables.

```{r}
summ <- c()

for(i in seq_along(cols_submodel)){
  summ[i] <- gen_compare_plot(sub1, cols_submodel[i])
}

print(length(summ))
```


### 2.

```{r}
summ <- c()

for(i in seq_along(cols_submodel)){
  summ[i] <- gen_compare_plot(sub2, cols_submodel[i])
}

print(length(summ))
```

## 3.

```{r}
summ <- c()

for(i in seq_along(cols_submodel)){
  summ[i] <- gen_compare_plot(sub3, cols_submodel[i])
}

print(length(summ))
```

## 4.

```{r}
summ <- c()

for(i in seq_along(cols_submodel)){
  summ[i] <- gen_compare_plot(sub4, cols_submodel[i])
}

print(length(summ))
```

```{r}

```

