---
title: "EDA case B"
output:
  pdf_document: default
  html_document: default
---

# Basic EDA for case study B
## Telco

```{r include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r, echo=FALSE, include=FALSE}
library(tidyverse)
library(readxl)
library(ggpubr)
library(corrr)
library(GGally)
library(dplyr)
library(gridExtra)
```

Updated EDA with Vivian's model
```{r}
# Add the new column (clusters_hc1 already in env)
#telco$group = clusters_hc1 
#head(telco) #yikes 25 cols
#write.csv(telco, file="grouped_telco.csv")

telco <- read.csv("4_groups_telco.csv")

telco$group <- as.factor(telco$group)
str(telco)
```

```{r}
# Sanity check
summary(telco)
telco[1,]
telco[, ncol(telco)]
str(telco)
```

Cols:       
1-2: basic customer info        
3-19: call data (duration)      
20-24: tariff schemes (cost)        

All variables are numeric.

```{r, echo=FALSE, include=FALSE}
telco[!complete.cases(telco),]
```
We have no NAs.

### Overall

```{r}
#pairs_tot <- ggpairs(telco, aes(color = group, alpha = 0.4))
#pairs_tot
```

```{r}
#pairs1_2 <- ggpairs(telco[, c(1:2, 25)], aes(color = group, alpha = 0.4))
#pairs1_2
#ggsave(gsub(" ", "", paste("figures/pairs/gp_pairs1_2.png")), width=10, height=6, units="in")
```


```{r}
#It's quite slow..
#pairs3_19 <- ggpairs(telco[, c(3:19, 25)], aes(color = group, alpha = 0.4))
#pairs3_19
#ggsave(gsub(" ", "", paste("figures/pairs/gp_pairs3_19.png")), width=30, height=18, units="in")
```

`Nat_call_cost_Sum`, `National_mins`, `All_calls_mins` -> multinomial distrib?

```{r}
# pairs20_24 <- ggpairs(telco[, 20:25], aes(color = group, alpha = 0.4))
# pairs20_24
# ggsave(gsub(" ", "", paste("figures/pairs/gp_pairs20_24.png")), width=6.5, height=4.5, units="in")
```

--> No more subset

### Misc

A few subsets to use.

```{r}
sub1_2 <- telco[, c(1:2, 25)]
sub3_19 <- telco[, c(3:19, 25)]
sub20_24 <- telco[, c(20:25)]

# Per groups
sub1 <- telco[which(telco$group==1),]
sub2 <- telco[which(telco$group==2),]
sub3 <- telco[which(telco$group==3),]
sub4 <- telco[which(telco$group==4),]


## No more submodel

# From the model (only the interesting variables)
#names <- as.vector(colnames(data_norm))
#names <- c("group", "Peak_calls_Sum", "Peak_mins_Sum", "OffPeak_calls_Sum", "OffPeak_mins_Sum", "International_mins_Sum", "Nat_call_cost_Sum", "National_calls", "National_mins", "All_calls_mins", "Mins_charge", "call_cost_per_min", "actual.call.cost", "Total_call_cost", "Total_Cost", "average_cost_min")
#names[12] <- "actual.call.cost"
#submodel <- telco %>% select(all_of(names))
```

## Groups comparison

```{r}
# delete "group" col to avoid errors 
cols_submodel <- colnames(telco)[-25]
```

### General
```{r}
ggplot(data = telco, aes(x = group, fill = group)) + geom_bar() +
  scale_fill_viridis_d() +
  ggsave("figures/barplot_groups.png")
```


### Histograms

```{r}
hist_col <- function (data, column) {
    if(class(column) == "factor"){
      stop("Factor")
    }
  ggplot(data = data, aes_string(x = column, color = data$group)) +
      geom_freqpoly(binwidth = 30) +
      xlab(column) +
      labs(title=paste0(column)) +
    ggsave(gsub(" ", "", paste("figures/hist/hist_", column, ".png")))
}
```

```{r}
histograms <- lapply(cols_submodel, hist_col, data = telco)

histograms
```


### Boxplots

```{r}
box_col <- function (data, column) {
  ggplot(data = data, aes_string(x = column, y = data$group)) +
    geom_boxplot(mapping = aes(color = group)) + xlab(column) + ylab("groups")  +
    labs(title = paste0(column)) +
    ggsave(gsub(" ", "", paste(
      "figures/boxplots/bxplt_", column, ".png"
    )), width = 2, height = 2)
}
```

```{r}
boxplots <- lapply(cols_submodel, box_col, data = telco)

boxplots
```

```{r}
# Specific plots for report
fig1 = telco %>% select("group",
                        "All_calls_mins",
                        "OffPeak_mins_Sum",
                        "Peak_mins_Sum")
#fig1[, 2:4] <- apply(fig1[, 2:4], 2, FUN=scale)

fig1_long <- fig1 %>%
  gather(key,
         value,
         c("All_calls_mins", "OffPeak_mins_Sum", "Peak_mins_Sum"))

ggplot(data = fig1_long, aes(x = value, y = group, fill = group)) +
  geom_boxplot() + facet_wrap( ~key, scales="free_x") + scale_y_discrete(limits=rev) +
  theme_minimal() +
  ggsave(gsub(" ", "", paste(
    "figures/boxplots/bxplt_fig1.png"
  )), width = 6, height = 3)

```

```{r}
fig2 = telco %>% select("group",
                        "OffPeak_calls_Sum",
                        "Peak_calls_Sum")
#fig2[, 2:3] <- apply(fig2[, 2:3], 2, FUN=scale)

fig2_long <- fig2 %>%
  gather(key,
         value,
         c("OffPeak_calls_Sum", "Peak_calls_Sum"))

ggplot(data = fig2_long, aes(x = value, y = group, fill = group)) +
  geom_boxplot() + facet_wrap( ~key, scales="free_x") + scale_y_discrete(limits=rev) +
  theme_minimal() +
  ggsave(gsub(" ", "", paste(
    "figures/boxplots/bxplt_fig2.png"
  )), width = 5, height = 3)
```

```{r}
fig3 = telco %>% select("group",
                        "National_mins",
                        "International_mins_Sum",
                        "National_calls")
#fig3[, 2:4] <- apply(fig3[, 2:4], 2, FUN=scale)

fig3_long <- fig3 %>%
  gather(key,
         value,
         c("National_mins",
           "International_mins_Sum",
           "National_calls"))

ggplot(data = fig3_long, aes(x = value, y = group, fill = group)) +
  geom_boxplot() + facet_wrap(~key, ncol=4, scales="free_x") + scale_y_discrete(limits = rev) +
  theme_minimal() +
  ggsave(gsub(" ", "", paste("figures/boxplots/bxplt_fig3.png")), width = 6, height = 3)

#ggplot(data = fig3_long, aes(x = value, y = key, fill = group)) +
#  geom_boxplot() + facet_wrap(~group, ncol=4) + scale_y_discrete(limits = #rev) +
#  theme_minimal() +
#  ggsave(gsub(" ", "", paste("figures/boxplots/bxplt_fig3.png")), width = #6, height = 3)
```

```{r}
fig4.2 = telco %>% select(
  "group",
  "Nat_call_cost_Sum",
  "actual.call.cost",
  "Mins_charge",
  "call_cost_per_min"
)
#fig4.2[, 2:3] <- apply(fig4.2[, 2:3], 2, FUN = scale)

fig4.2_long <- fig4.2 %>%
  gather(
    key,
    value,
    c(
      "Nat_call_cost_Sum",
      "actual.call.cost",
      "Mins_charge",
      "call_cost_per_min"
    )
  )

ggplot(data = fig4.2_long, aes(x = value, y = group, fill = group)) +
  geom_boxplot() + facet_wrap( ~ key, ncol=4, scales="free_x") + scale_y_discrete(limits = rev) +
  theme_minimal() +
  ggsave(gsub(" ", "", paste("figures/boxplots/bxplt_fig42.png")), width = 7, height = 3)

```

```{r}
fig6 = telco %>% select("group",
                        "average_cost_min",
                        "Total_Cost",
                        "Total_call_cost")
#fig6[, 2:4] <- apply(fig6[, 2:4], 2, FUN=scale)

fig6_long <- fig6 %>%
  gather(key,
         value,
         c("average_cost_min",
           "Total_Cost",
           "Total_call_cost"))

ggplot(data = fig6_long, aes(x = value, y = group, fill = group)) +
  geom_boxplot() + facet_wrap( ~ key, scales="free_x") + scale_y_discrete(limits = rev) +
  theme_minimal() +
  ggsave(gsub(" ", "", paste("figures/boxplots/bxplt_fig6.png")), width = 6, height = 3)

```

```{r}
telco.scaled <- telco
telco.scaled[, 1:24] <- apply(telco.scaled[, 1:24], 2, FUN=scale)

summ.fig.long <- telco.scaled %>%
  gather(key,
         value,
        names(telco)[names(telco) != "group"])

ggplot(data = summ.fig.long, aes(x = value, y = key, fill = group)) +
  geom_boxplot() + facet_wrap( ~ group, ncol=4) + scale_y_discrete(limits = rev) +
  theme_minimal() +
  ggsave(gsub(" ", "", paste("figures/boxplots/bxplt_summfig.png")), width = 6, height = 3)

#ggplot(data = fig3_long, aes(x = value, y = key, fill = group)) +
#  geom_boxplot() + facet_wrap(~group, ncol=4) + scale_y_discrete(limits = #rev) +
#  theme_minimal() +
#  ggsave(gsub(" ", "", paste("figures/boxplots/bxplt_fig3.png")), width = #6, height = 3)
```


## Groupwise EDA

Perform a small EDA for each group to see if we can extract some obvious features.

Let's recall the overall summary:
```{r}
# Color per group
gp_cols <- c("#F8766D", "#B79F00", "#00BA38", "#00BFC4")
```

```{r}
# Compare the median of the subgroup
# wrt to base
gen_compare_med <- function(summ, base){
  med1 <- summ[[3]]
  med2 <- base[[3]]
  base_1qr <- base[[2]]
  base_3qr <- base[[5]]

  #print(paste("med1", med1))
  #print(paste("med2", med2))
  
  if(med1 > base_3qr){
    print("Bigger than 3rd base quartile")
  }
  else if(med1 >= med2){
    print("Bigger than base median")
  }
  else if(med1 <= med2){
    if(med1 < base_1qr){
      print("Smaller than 1st base quartile")
    }
    else{
      print("Smaller than base median") 
    }
  }
}
```

```{r}
# Dynamically create 2 boxplots to compare
gen_compare_plot <- function(subgroup, col, summary=FALSE){
  group_nb <- subgroup$group[1]
  ymin <- min(telco[, col]) - .1 * min(telco[, col])
  ymax <- 1.1 * max(telco[, col])
  
  b1 <- ggplot(data=subgroup, aes_string(y = subgroup[, col], x=subgroup$group, fill=subgroup$group)) + ylim(c(ymin, ymax)) + geom_boxplot(width=0.4)
  
  b2 <- ggplot(data=telco, aes_string(y = telco[, col], x = group_nb)) + ylim(c(ymin, ymax)) + geom_boxplot(width=0.4)
  
  grid.arrange(b1, b2, ncol=2, top=paste("group", group_nb, col))
  g <- arrangeGrob(b1, b2, ncol=2, top=paste("group", group_nb, col))
  ggsave(gsub(" ", "", paste("figures/boxplots/compare/", group_nb, "_", col, ".png")), g, width=10, height=6.3, units="in")
  
  # Compare the medians
  med_compar <- gen_compare_med(summary(subgroup[, col]), summary(telco[, col]))
  
  return(med_compar)
}

```

### 1.

For each variable, check the boxplot (`figures/boxplots`). Let's focus on the model variables.

```{r}
summ <- c()

for(i in seq_along(cols_submodel)){
  summ[i] <- gen_compare_plot(sub1, cols_submodel[i])
}

print(length(summ))
```


### 2.

```{r}
summ <- c()

for(i in seq_along(cols_submodel)){
  summ[i] <- gen_compare_plot(sub2, cols_submodel[i])
}

print(length(summ))
```

## 3.

```{r}
summ <- c()

for(i in seq_along(cols_submodel)){
  summ[i] <- gen_compare_plot(sub3, cols_submodel[i])
}

print(length(summ))
```

## 4.

```{r}
summ <- c()

for(i in seq_along(cols_submodel)){
  summ[i] <- gen_compare_plot(sub4, cols_submodel[i])
}

print(length(summ))
```

```{r}

```

