---
title: "Untitled"
author: "Vivian Carranza"
date: "25/4/2021"
output: html_document
---

```{r, results='hide', message=FALSE, warning= FALSE}

library(factoextra)
library(reshape2)
library(ggplot2)
library(FNN)
library(caret)
library(readxl)
library(corrplot)
library(cluster)


library(knitr)
library(olsrr)
library(corrplot)
library(nortest)
library(reghelper)
library(psych)
library(QuantPsyc)
library(REdaS)
library(tidyr)
library(ggplot2)

telco_data <- read_excel("Btelco.xls") #na.omit(read.csv("Cereals.csv", header = T, sep = ","))

```



1. Data Pre-Processing
2. Initial variable selection (PCA)

```{r}
bart_spher(telco_data)

fa.parallel(telco_data, n.obs=916, fa="pc", n.iter=100,main="Scree plots with parallel analysis")
FA0 <- fa(telco_data, rotate="varimax",nfactors=24, scores=TRUE)

png("figures/scree_plot.png",width=750)
plot(FA0$values ,xlab="Factor Number",ylab="Eigenvalue",main="Scree plot",cex.lab=1.2,cex.axis=1.2,cex.main=1.8)+abline(h=1)
dev.off()
plot(FA0$values ,xlab="Factor Number",ylab="Eigenvalue",main="Scree plot",cex.lab=1.2,cex.axis=1.2,cex.main=1.8)+abline(h=1)

pc <- principal(telco_data, rotate="varimax",nfactors=6, scores=TRUE)
print(pc$loadings, cutoff=0.55,sort=TRUE)

```

3. Correlation plot and scaling 
```{r, fig.width=14, fig.height=12}
datos_telco <- telco_data
drop_pca <- c("Age","L_O_S","Dropped_Calls")
drop <- c(drop_pca)
  #c("Age","AveWeekend","AveOffPeak","AvePeak","Weekend_calls_Sum","L_O_S","AveNational","Weekend_mins_Sum","Dropped_Calls")
datos <- datos_telco[,!(names(datos_telco) %in% drop)]
#datos <- datos_telco

#cor(datos)
corr <- round(cor(datos, method = "spearman"),1)
corrplot(corr, method = "square")

#Normalize 
data_norm <- preProcess(datos, method="range")
data_norm <- predict(data_norm, datos)
#data_norm <- scale(datos)
#row.names(data_norm) <- datos[,1]

#Distances
d.norm <- dist(data_norm, method = "euclidean")
#fviz_dist(d.norm, gradient = list(low = "#00AFBB", mid = "white", high = "#FC4E07"))

```


4. Assessing clustering tendency 
```{r}
#Assessing clustering tendency 
gradient.color <- list(low = "steelblue",  high = "white")

data_norm %>% get_clust_tendency(n = 50, gradient = gradient.color)

```

5. Optimal number of clusters (Why to choose 4 instead of 6) 
```{r}
#Optimal number of clusters
#fviz_nbclust(data_norm, hcut, method = "gap_stat")
gap_stat <- clusGap(data_norm, FUN = hcut, K.max = 10, B = 10)
png("figures/4_clusters.png",width=750)
print(gap_stat, method = "firstmax")
fviz_gap_stat(gap_stat)
dev.off()
fviz_gap_stat(gap_stat)
```


6. Initial Distribution of the clusters (analysis of the groups, with the boxplot or the barplot)
```{r, fig.width=14}

#Single Linkage
hc1 <- hclust(d.norm, method = "ward.D2")

#Centroides Single Linkage 
clusters_hc1 <- cutree(hc1, k = 4)
centroide_hc1 <- aggregate(data_norm, by = list(clusters_hc1), FUN = mean) 
centroide_hc1 <- round(centroide_hc1,2)

centroide_hc1 <- melt(data = centroide_hc1[,1:ncol(centroide_hc1)], id.vars = "Group.1")

ggplot(centroide_hc1, aes(x = variable, y = value, group = Group.1, color = factor(Group.1), size = 1)) +
    geom_line(size=0.5)+
    theme(axis.text.x = element_text(angle = 90))

centroide_hc1
#clusters_hc1

clusplot(data_norm, clusters_hc1, color=TRUE, shade=TRUE, lines=0, labels = 4)

```

7. Second variable selection (to improve the variability intra-groups) 
```{r}
#Variable selection
centroide_hc <- aggregate(data_norm, by = list(clusters_hc1), FUN = mean) 
centroide_hc <- round(centroide_hc,2)
centroide_transpose <- as.data.frame(t(as.matrix(centroide_hc)))
centroide_transpose <- transform(centroide_transpose, SD=apply(centroide_transpose,1, sd, na.rm = TRUE))
drop <- row.names(centroide_transpose)[which(centroide_transpose$SD<0.1)] 


#drop <- c("AveWeekend","AveOffPeak","AvePeak","Weekend_calls_Sum","AveNational","Weekend_mins_Sum")
data_norm <- data_norm[,!(names(data_norm) %in% drop)]
#Distances
d.norm <- dist(data_norm, method = "euclidean")

#Single Linkage
hc1 <- hclust(d.norm, method = "ward.D2")

#Centroides Single Linkage 
clusters_hc1 <- cutree(hc1, k = 6)
centroide_hc1 <- aggregate(data_norm, by = list(clusters_hc1), FUN = mean) 
centroide_hc1 <- round(centroide_hc1,2)

centroide_hc1 <- melt(data = centroide_hc1[,1:ncol(centroide_hc1)], id.vars = "Group.1")

ggplot(centroide_hc1, aes(x = variable, y = value, group = Group.1, color = factor(Group.1), size = 1)) +
    geom_line(size=0.5)+
    theme(axis.text.x = element_text(angle = 90))

centroide_hc1
#clusters_hc1

clusplot(data_norm, clusters_hc1, color=TRUE, shade=TRUE, lines=0, labels = 4)

```


7. Measurement (Within cluster sum of squares by cluster)

8. Customer profiling 

```{r}
datos <- data.frame(average_cost_min= telco_data$average_cost_min, 
                    AveNational= telco_data$AveNational, 
                    Dropped_Calls= telco_data$Dropped_Calls, 
                    AveOffPeak= telco_data$AveOffPeak, 
                    AvePeak= telco_data$AvePeak, 
                    AveWeekend= telco_data$AveWeekend, 
                    call_cost_per_min= telco_data$call_cost_per_min, 
                    actual_call_cost= telco_data$`actual call cost`,
                    Nat_call_cost_Sum= telco_data$Nat_call_cost_Sum,
                    Weekend_calls_Sum= telco_data$Weekend_calls_Sum,
                    Age= telco_data$Age,
                    L_O_S= telco_data$L_O_S, 
                    Weekend_mins_Sum= telco_data$Weekend_mins_Sum
                    )


datos <-  cbind(clusters_hc1,datos)
colnames(datos)[1] <- "Group"
group_means <- aggregate(datos, by = list(clusters_hc1), FUN = mean)
group_means <- group_means[,!(names(group_means) %in% "Group")]


means <- as.data.frame(colMeans(datos))
colnames(means) <- c("values")
means <- data.frame(variable = colnames(group_means), value = means$values)
means <- means[-1,]

plotdata <- gather(group_means, key="variable", value="value", -Group.1)
ggplot(data = plotdata, aes(variable, value, fill = variable), ylab = "mean") + 
  geom_bar(stat="identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position="none") +  
  coord_flip() +
  facet_wrap(~ Group.1, ncol = 4) +
  scale_fill_viridis_d(begin = 0.2, end = 0.85)+
  geom_point(data = means, col = 'red') +
  ggsave("figures/facet_wrap_6.png",width=7.5)

```

```{r}
datos <- data.frame(Peak_calls_Sum= telco_data$Peak_calls_Sum, 
                    OffPeak_mins_Sum= telco_data$OffPeak_mins_Sum, 
                    National_calls= telco_data$National_calls, 
                    Peak_mins_Sum= telco_data$Peak_mins_Sum, 
                    National_mins= telco_data$National_mins, 
                    All_calls_mins= telco_data$All_calls_mins, 
                    Mins_charge= telco_data$Mins_charge,
                    Total_call_cost= telco_data$Total_call_cost,
                    International_mins_Sum= telco_data$International_mins_Sum,
                    OffPeak_calls_Sum= telco_data$OffPeak_calls_Sum,
                    Total_Cost= telco_data$Total_Cost
                    )

datos <- cbind(clusters_hc1,datos)
colnames(datos)[1] <- "Group"
group_means <- aggregate(datos, by = list(clusters_hc1), FUN = mean)
group_means <- group_means[,!(names(group_means) %in% "Group")]


means <- as.data.frame(colMeans(datos))
colnames(means) <- c("values")
means <- data.frame(variable = colnames(group_means), value = means$values)
means <- means[-1,]

plotdata <- gather(group_means, key="variable", value="value", -Group.1)
ggplot(data = plotdata, aes(variable, value, fill = variable), ylab = "mean") + 
  geom_bar(stat="identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position="none") +  
  coord_flip() +
  facet_wrap(~ Group.1, ncol = 4) +
  scale_fill_viridis_d(begin = 0.2, end = 0.85)+
  geom_point(data = means, col = 'red') +
  ggsave("figures/facet_wrap_selected_6.png",width=7.5)
```

