---
title: "EDA 2"
author: "Sneha Santha Prabakar"
date: "3/17/2021"
output:
  pdf_document: default
  html_document: default
  word_document: default
---


```{r}
library(readxl)
library(ggplot2)
library(reshape2)
library(stringr)
library(ggrepel)
```


```{r}
setwd("~")
df = read_excel("Aclothing.xls")
str(df)
```

# 1. Check for NA

```{r}
na_columns = colnames(df)[apply(df, 2, anyNA)]
na_columns
num_records = dim(df)[1]
```

No NA values in the dataset

# 2. Distribution of each variable

### 2.1. Clothing

```{r}
clothing_type_count = table(df$Clothing)
clothing_type_count = melt(clothing_type_count)
colnames(clothing_type_count)[1] = "Clothing_Type"
colnames(clothing_type_count)[2] = "Frequency"
clothing_type_count$Percentage = round(((clothing_type_count$Frequency)/num_records)*100, 1)
```

```{r}
ggplot(data = clothing_type_count, 
       aes(x = Clothing_Type, y = Percentage, fill = Percentage))+
  geom_bar(stat = "identity") + scale_fill_viridis_b(direction=-1, option="cividis") + xlab("Clothing type") + geom_text(aes(x=Clothing_Type, y=Percentage, label=paste(Percentage, "%")), position=position_dodge(width=1), vjust=-0.5, size=3) + theme(panel.background = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour="black")) + labs(fill = "Percentage of students (in %)") + ylab("Percentage of students")+ ggtitle("Distribution of Clothing Type amongst all students") + theme(plot.title = element_text(hjust = 0.5, face="bold.italic", size=14))
```


### 2.2. Gender

```{r}
gender_count = table(df$Gender)
gender_count = melt(gender_count)
colnames(gender_count)[1] = "Gender"
colnames(gender_count)[2] = "Frequency"
gender_count$Percentage = round(((gender_count$Frequency)/num_records)*100, 1)
gender_count
```

```{r}
ggplot(data = gender_count, 
       aes(x = Gender, y = Percentage, fill = Percentage))+
  geom_bar(stat = "identity") + scale_fill_viridis_b(direction=-1, option="cividis") + xlab("Gender") + geom_text(aes(x=Gender, y=Percentage, label=paste(Percentage, "%")), position=position_dodge(width=1), vjust=-0.5, size=3) + theme(panel.background = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour="black")) + labs(fill = "Percentage of students") + ylab("Percentage of students (in %)")+ ggtitle("Distribution of Gender amongst all students") + theme(plot.title = element_text(hjust = 0.5, face="bold.italic", size=14))
```

### 2.3. Count of interactions

```{r}
count_distr = table(df$Count)
count_distr = melt(count_distr)
colnames(count_distr)[1] = "Number_of_interactions"
colnames(count_distr)[2] = "Frequency"
#plot(count_distr, lwd=5, pch=15, type="b")
ggplot(data=count_distr, aes(x=Number_of_interactions, y=Frequency)) + geom_point() + geom_line() + xlab("Number of interactions") + ylab("Frequency") + geom_text(aes(label=Frequency), vjust=-1.5, hjust=-0.5) + ylim(0, 210) + ggtitle(str_wrap("Distribution of number of interactions between each student and the teacher", width=50)) + theme(plot.title = element_text(hjust = 0.5, face="bold.italic", size=14))+ theme(panel.background = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour="black"))
```

### 2.4. Type of interactions

```{r}
type_intr = table(df$InteractionType)
type_intr = melt(type_intr)
colnames(type_intr)[1] = "Type_of_Interaction"
colnames(type_intr)[2] = "Frequency"
type_intr$Percentage = round(((type_intr$Frequency)/num_records)*100, 1)
type_intr
```

```{r}
ggplot(data = type_intr, 
       aes(x = Type_of_Interaction, y = Percentage, fill=Percentage))+
  geom_bar(stat = "identity") + xlab("Type of interaction") + geom_text(aes(x=Type_of_Interaction, y=Percentage, label=paste(Percentage, "%")), position=position_dodge(width=1), vjust=-0.5, size=3) + theme(panel.background = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour="black"), legend.position = "none") + labs(fill = "Percentage of students") + ylab("Percentage of students (in %)")+ ggtitle("Distribution of Type of interaction with all students") + theme(plot.title = element_text(hjust = 0.5, face="bold.italic", size=14))
```

We can see that the data is evenly distributed - with equal number of observations for both the types of interaction. 

# 3. Data Visualization

### 3.1. Gender and Interaction type 

```{r}
gender_intr = table(df$Gender, df$InteractionType)
gender_intr = melt(gender_intr)
colnames(gender_intr)[1] = "Gender"
colnames(gender_intr)[2] = "Type_Interaction"
gender_intr$Percentage = round(((gender_intr$value)/num_records)*100, 1)
```

```{r}
ggplot(gender_intr, aes(fill=Type_Interaction, y=Percentage, x=Gender)) + 
    geom_bar(stat="identity") + geom_text(aes(x=Gender, y=Percentage, label=paste(Percentage, "%")), size=5, color="red", position = position_stack(vjust=0.5)) + theme(panel.background = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour="black")) + labs(fill = "Type of Interaction") + ylab("Percentage of students (in %)")+ ggtitle("Type of interactions by Gender") + theme(plot.title = element_text(hjust = 0.5, face="bold.italic", size=14)) + scale_fill_viridis_d(direction=-1, option="cividis")
```

### 3.2. Clothing and Interaction type

```{r}
clothing_intr = table(df$Clothing, df$InteractionType)
clothing_intr = melt(clothing_intr)
colnames(clothing_intr)[1] = "Clothing_Type"
colnames(clothing_intr)[2] = "Type_Interaction"
clothing_intr$Percentage = round(((clothing_intr$value)/num_records)*100, 1)
```

```{r}
ggplot(clothing_intr, aes(fill=Type_Interaction, y=Percentage, x=Clothing_Type)) + 
    geom_bar(stat="identity") + geom_text(aes(x=Clothing_Type, y=Percentage, label=paste(Percentage, "%")), size=5, color="red", position = position_stack(vjust=0.5)) + theme(panel.background = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour="black")) + labs(fill = "Type of Interaction") + ylab("Percentage of students (in %)")+ ggtitle("Type of interactions by Clothing Type") + theme(plot.title = element_text(hjust = 0.5, face="bold.italic", size=14)) + scale_fill_viridis_d(direction=-1, option="cividis")
```

### 3.3. Count of interactions and Interaction type

```{r}
count_intr = table(df$Count, df$InteractionType)
count_intr = melt(count_intr)
colnames(count_intr)[1] = "Count"
colnames(count_intr)[2] = "Type_Interaction"
count_intr$Percentage = round(((count_intr$value)/num_records)*100, 1)
count_intr
```
```{r}
ggplot(count_intr, aes(fill=Type_Interaction, y=Percentage, x=as.factor(Count))) + 
    geom_bar(stat="identity") + geom_text_repel(aes(x=as.factor(Count), y=Percentage, label=paste(Percentage, "%")), size=2, color="red", position = position_stack(vjust=0.15)) + theme(panel.background = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour="black")) + labs(fill = "Type of Interaction") + ylab("Percentage of students (in %)")+ ggtitle("Type of interactions by Number of interactions with each student") + theme(plot.title = element_text(hjust = 0.5, face="bold.italic", size=14)) + coord_flip() + xlab("Number of interactions with a student") + scale_fill_viridis_d(direction=-1, option="cividis")
```

We can make the following preliminary observations based on Figure 3.1 to 3.3:

1. No influence of gender on the type of interaction - as each gender has equal distribution of positive and negative interactions
2. No influence of clothing type on the type of interaction - as each clothing type has equal distribution of positive and negative interactions
3. There is significant influence of the count of interaction on the type of interaction - as the distribution of positive and negative interaction varies significant for each count

Hence, let us now look for any cross-relationship between the count of interaction and gender/clothing type

# 4. Cross-relationship between the count of interaction and gender/clothing type

```{r}
all_three_var = table(df$Count, df$Gender, df$Clothing)
all_three_var = melt(all_three_var)
colnames(all_three_var)[1] = "Count"
colnames(all_three_var)[2] = "Gender"
colnames(all_three_var)[3] = "Clothing_Type"
all_three_var$Percentage = round(((all_three_var$value)/num_records)*100, 1)
all_three_var[all_three_var$Gender=="Male",]
```

```{r, fig.width=6}
ggplot(data=all_three_var[all_three_var$Gender=="Male",], aes(x=Percentage, y=as.factor(Count), color=Clothing_Type)) + geom_point(size=3) + theme(panel.background = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour="black")) + xlab("Percentage of students (in %)")+ ylab("Count of interactions") + ggtitle(str_wrap("Cross-relationship between Count of interactions and Clothing Type (for Male students)", width=50)) + theme(plot.title = element_text(hjust = 0.5, face="bold.italic", size=14)) + theme(axis.text.y = element_text(angle = 90, vjust = 0.5)) + scale_color_viridis_d(direction=-1, option="cividis")
```


```{r, fig.width=6}
# use as.factor() to display all values of the column in the specific axis
ggplot(data=all_three_var[all_three_var$Gender=="Female",], aes(x=Percentage, y=as.factor(Count), color=Clothing_Type), shape=17) + geom_point(size=3) + theme(panel.background = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour="black")) + xlab("Percentage of students (in %)")+ ylab("Count of interactions") + ggtitle(str_wrap("Cross-relationship between Count of interactions and Clothing Type (for Female students)", width=50)) + theme(plot.title = element_text(hjust = 0.5, face="bold.italic", size=14)) + theme(axis.text.y = element_text(angle = 90, vjust = 0.5)) + scale_color_viridis_d(direction=-1, option="cividis")
```


Comparing the two graphs above, we can see that:

1. For both genders, the students having clothing type = "Other" have maximum of 9 interactions only. 
2. In Male students, there is a relatively more equal mix of Std and Unisex clothing types for more those who have had more than 10 interactions. Whereas, in Female students, a clear majority of students who have had more than 10 interactions are only those with Unisex clothing types.
3. In Female students, the lowest share of students at almost every interaction are the ones with Unisex clothing (except only 3 occurrences). Whereas in Male students, it is more evenly distributed between students with Std and Unisex clothing. However, in both cases, there is only 1 occurence (count = 7 for Female students, and count = 4 for Male students) when the lowest share of students are those with Other type of clothing.


# Model building


*Model 1: For Interaction Type*

```{r}
df$InteractionType = as.factor(df$InteractionType)

logistic_reg_model = glm(InteractionType~., data=df, family="binomial")
logistic_reg_model
```

*Model 2: For count of interactions*

```{r}
df_2 = df[,-4]
df_2$Clothing = transform(df_2$Clothing,id=as.numeric(factor(df_2$Clothing)))$id
df_2$Gender = transform(df_2$Gender,id=as.numeric(factor(df_2$Gender)))$id

model2 = lm(Count~., data=df_2)
summary(model2)
```

