---
title: "Case Study C"
author: "Hervégil Voegeli"
date: "13/04/2021"
output: html_document
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r}

setwd("E:/Universite de Genève/Faculté d'économie/Mon Master en statistique/A1S2/Analytics Consulting/analytics-consulting/C")

```


```{r, echo=FALSE, include=FALSE}
library(tidyverse)
library(readxl)
library(ggpubr)
library(corrr)
library(GGally)
library(dplyr)
library(gridExtra)
library(reshape2)
```


```{r}

head <- read_excel("Cheadinjury.xls",col_types = "text")


attach(head)

str(head)

```

```{r}
hist_col <- function (data, column) {
  ggplot(data = data, aes(column)) +
      geom_histogram(stat="count") +
      xlab(column) +
      labs(title=paste0(column)) +
    ggsave(gsub(" ", "", paste("figures/histograms/hist_", column, ".png")))
}
```

```{r}
head %>%
  ggplot(aes(x=age.65)) +
  geom_histogram(stat = "count") +
  xlab("age.65") +
  labs(title = "age.65") +
  ggsave(paste0("figures/histograms/hist_", "age.65", ".png"))

head %>%
  ggplot(aes(x=amnesia.before)) +
  geom_histogram(stat = "count") +
  xlab("amnesia.before") +
  labs(title = "amnesia.before") +
  ggsave(paste0("figures/histograms/hist_", "amnesia.before", ".png"))

head %>%
  ggplot(aes(x=basal.skull.fracture)) +
  geom_histogram(stat = "count") +
  xlab("basal.skull.fracture") +
  labs(title = "basal.skull.fracture") +
  ggsave(paste0("figures/histograms/hist_", "basal.skull.fracture", ".png"))


head %>%
  ggplot(aes(x=GCS.decrease)) +
  geom_histogram(stat = "count") +
  xlab("GCS.decrease") +
  labs(title = "GCS.decrease") +
  ggsave(paste0("figures/histograms/hist_", "GCS.decrease", ".png"))


head %>%
  ggplot(aes(x=GCS.13)) +
  geom_histogram(stat = "count") +
  xlab("GCS.13") +
  labs(title = "GCS.13") +
  ggsave(paste0("figures/histograms/hist_", "GCS.13", ".png"))


head %>%
  ggplot(aes(x=GCS.15.2hours)) +
  geom_histogram(stat = "count") +
  xlab("GCS.15.2hours") +
  labs(title = "GCS.15.2hours") +
  ggsave(paste0("figures/histograms/hist_", "GCS.15.2hours", ".png"))


head %>%
  ggplot(aes(x=high.risk)) +
  geom_histogram(stat = "count") +
  xlab("high.risk") +
  labs(title = "high.risk") +
  ggsave(paste0("figures/histograms/hist_", "high.risk", ".png"))


head %>%
  ggplot(aes(x=loss.of.consciousness)) +
  geom_histogram(stat = "count") +
  xlab("loss.of.consciousness") +
  labs(title = "loss.of.consciousness") +
  ggsave(paste0("figures/histograms/hist_", "loss.of.consciousness", ".png"))


head %>%
  ggplot(aes(x=open.skull.fracture)) +
  geom_histogram(stat = "count") +
  xlab("open.skull.fracture") +
  labs(title = "open.skull.fracture") +
  ggsave(paste0("figures/histograms/hist_", "open.skull.fracture", ".png"))


head %>%
  ggplot(aes(x=vomiting)) +
  geom_histogram(stat = "count") +
  xlab("vomiting") +
  labs(title = "vomiting") +
  ggsave(paste0("figures/histograms/hist_", "vomiting", ".png"))

clin = sum(head$clinically.important.brain.injury==0)
no_clin = sum(head$clinically.important.brain.injury==1)

head %>%
  ggplot(aes(x = clinically.important.brain.injury,fill=clinically.important.brain.injury)) +
  geom_histogram(stat = "count") +
  labs(title = "Patients having a clinically important brain injury",
       y="Number of patients") +
  scale_x_discrete(name ="Clinically important brain injury",labels=c("no","yes")) +
  theme_classic()+
  scale_fill_viridis_d(direction=-1, option="cividis")+
  theme(axis.text=element_text(size=14))+
  theme(legend.position = "none")+
  annotate(geom="text",x=1,y=clin-10,
           label= paste(clin),color="black",size=6,vjust=0)+
  annotate(geom="text",x=2,y=no_clin-10,
           label= paste(no_clin),color="black",size=6,vjust=0)+
  ggsave(paste0(
    "figures/histograms/hist_",
    "clinically.important.brain.injury",
    ".png"),height=7,width=5)

clin = sum(head$clinically.important.brain.injury==0&head$high.risk==1)
no_clin = sum(head$clinically.important.brain.injury==1&head$high.risk==1)

head %>%
  filter(high.risk==1) %>% 
  ggplot(aes(x = clinically.important.brain.injury,fill=clinically.important.brain.injury)) +
  geom_histogram(stat = "count") +
  labs(title = "High risk patients having a clinically important brain injury",
       y="Number of patients") +
  scale_x_discrete(name ="Clinically important brain injury",labels=c("no","yes")) +
  theme_classic()+
  scale_fill_viridis_d(direction=-1, option="cividis")+
  theme(axis.text=element_text(size=14))+
  theme(legend.position = "none")+
  annotate(geom="text",x=1,y=clin-10,
           label= paste(clin),color="black",size=6,vjust=0)+
  annotate(geom="text",x=2,y=no_clin-10,
           label= paste(no_clin),color="black",size=6,vjust=0)+
  ggsave(paste0(
    "figures/histograms/hist_",
    "clinically.important.brain.injury_AND_high_risk",
    ".png"
  ),height=7,width=6)

```



```{r}


```




 Those percentages will be P(brain injury|variable X = {0 ; 1} AND individuals who suffered...)

 Why is that? Because this data was not collected on the population as a whole. We always have this condition individuals who suffered ‘minor’ head injuries) fulfilled.
 How is that a problem?
 ->Imagine the following situation:
 We are asked "what is the impact of eating an additional 100g of meat per day on B12 levels?" (B12 is only acquired through meat)
 1) If we measure this only on vegan people, and additional 100g will have a huge impact.
 2) If we measure this on people eating too much meat, this will have zero effect.

 Another funny example:
 Effects of eggs on your health is often controversed: 
 American studies show that it is bad for health while Asiatic ones show it is great.
 American studies are conducted on American people (logical) and Asiatic ones on Asiatic people.
 Not having the same population conducts different results.

 We will see later what impact it will have on our study.


```{r}
percent <- head %>%
  group_by(age.65) %>%
  summarise(injury_vs_age = round(sum(clinically.important.brain.injury == 1)/n(), 2) * 100)

head %>%
  ggplot(aes(x=age.65,fill=clinically.important.brain.injury)) +
  geom_histogram(stat = "count") +
  xlab("age.65") +
  labs(title = "age.65") +
  geom_text(aes(x=1,y=10),label=paste(percent[1,2],"% having injury")) +
  geom_text(aes(x=2,y=10),label=paste(percent[2,2],"% having injury")) +
  ggsave(paste0("figures/histograms/hist_", "age.65","_vs_brain.injury",".png"))

percent <- head %>%
  group_by(amnesia.before) %>%
  summarise(injury_vs_amnesia = round(sum(clinically.important.brain.injury == 1)/n(), 2) * 100)

head %>%
  ggplot(aes(x=amnesia.before,fill=clinically.important.brain.injury)) +
  geom_histogram(stat = "count") +
  xlab("amnesia.before") +
  labs(title = "amnesia.before") +
  geom_text(aes(x=1,y=10),label=paste(percent[1,2],"% having injury")) +
  geom_text(aes(x=2,y=10),label=paste(percent[2,2],"% having injury")) +
  ggsave(paste0("figures/histograms/hist_", "amnesia.before","_vs_brain.injury", ".png"))

percent <- head %>%
  group_by(basal.skull.fracture) %>%
  summarise(injury_vs_basal.skull.fracture = round(sum(clinically.important.brain.injury == 1)/n(), 2) * 100)

head %>%
  ggplot(aes(x=basal.skull.fracture,fill=clinically.important.brain.injury)) +
  geom_histogram(stat = "count") +
  xlab("basal.skull.fracture") +
  labs(title = "basal.skull.fracture") +
  geom_text(aes(x=1,y=10),label=paste(percent[1,2],"% having injury")) +
  geom_text(aes(x=2,y=10),label=paste(percent[2,2],"% having injury")) +
  ggsave(paste0("figures/histograms/hist_", "basal.skull.fracture","_vs_brain.injury", ".png"))

percent <- head %>%
  group_by(GCS.decrease) %>%
  summarise(injury_vs_GCS.decrease = round(sum(clinically.important.brain.injury == 1)/n(), 2) * 100)

head %>%
  ggplot(aes(x=GCS.decrease,fill=clinically.important.brain.injury)) +
  geom_histogram(stat = "count") +
  xlab("GCS.decrease") +
  labs(title = "GCS.decrease") +
  geom_text(aes(x=1,y=10),label=paste(percent[1,2],"% having injury")) +
  geom_text(aes(x=2,y=10),label=paste(percent[2,2],"% having injury")) +
  ggsave(paste0("figures/histograms/hist_", "GCS.decrease","_vs_brain.injury", ".png"))

percent <- head %>%
  group_by(GCS.13) %>%
  summarise(injury_vs_GCS.13 = round(sum(clinically.important.brain.injury == 1)/n(), 2) * 100)

head %>%
  ggplot(aes(x=GCS.13,fill=clinically.important.brain.injury)) +
  geom_histogram(stat = "count") +
  xlab("GCS.13") +
  labs(title = "GCS.13") +
  geom_text(aes(x=1,y=10),label=paste(percent[1,2],"% having injury")) +
  geom_text(aes(x=2,y=10),label=paste(percent[2,2],"% having injury")) +
  ggsave(paste0("figures/histograms/hist_", "GCS.13","_vs_brain.injury", ".png"))

percent <- head %>%
  group_by(GCS.15.2hours) %>%
  summarise(injury_vs_GCS.15.2hours = round(sum(clinically.important.brain.injury == 1)/n(), 2) * 100)

head %>%
  ggplot(aes(x=GCS.15.2hours,fill=clinically.important.brain.injury)) +
  geom_histogram(stat = "count") +
  xlab("GCS.15.2hours") +
  labs(title = "GCS.15.2hours") +
  geom_text(aes(x=1,y=10),label=paste(percent[1,2],"% having injury")) +
  geom_text(aes(x=2,y=10),label=paste(percent[2,2],"% having injury")) +
  ggsave(paste0("figures/histograms/hist_", "GCS.15.2hours","_vs_brain.injury", ".png"))

percent <- head %>%
  group_by(high.risk) %>%
  summarise(injury_vs_high.risk = round(sum(clinically.important.brain.injury == 1)/n(), 2) * 100)

head %>%
  ggplot(aes(x=high.risk,fill=clinically.important.brain.injury)) +
  geom_histogram(stat = "count") +
  xlab("high.risk") +
  labs(title = "high.risk") +
  geom_text(aes(x=1,y=10),label=paste(percent[1,2],"% having injury")) +
  geom_text(aes(x=2,y=10),label=paste(percent[2,2],"% having injury")) +
  ggsave(paste0("figures/histograms/hist_", "high.risk","_vs_brain.injury", ".png"))

percent <- head %>%
  group_by(loss.of.consciousness) %>%
  summarise(injury_vs_loss.of.consciousness = round(sum(clinically.important.brain.injury == 1)/n(), 2) * 100)

head %>%
  ggplot(aes(x=loss.of.consciousness,fill=clinically.important.brain.injury)) +
  geom_histogram(stat = "count") +
  xlab("loss.of.consciousness") +
  labs(title = "loss.of.consciousness") +
  geom_text(aes(x=1,y=10),label=paste(percent[1,2],"% having injury")) +
  geom_text(aes(x=2,y=10),label=paste(percent[2,2],"% having injury")) +
  ggsave(paste0("figures/histograms/hist_", "loss.of.consciousness","_vs_brain.injury", ".png"))

percent <- head %>%
  group_by(open.skull.fracture) %>%
  summarise(injury_vs_open.skull.fracture = round(sum(clinically.important.brain.injury == 1)/n(), 2) * 100)

head %>%
  ggplot(aes(x=open.skull.fracture,fill=clinically.important.brain.injury)) +
  geom_histogram(stat = "count") +
  xlab("open.skull.fracture") +
  labs(title = "open.skull.fracture") +
  geom_text(aes(x=1,y=10),label=paste(percent[1,2],"% having injury")) +
  geom_text(aes(x=2,y=10),label=paste(percent[2,2],"% having injury")) +
  ggsave(paste0("figures/histograms/hist_", "open.skull.fracture","_vs_brain.injury", ".png"))

percent <- head %>%
  group_by(vomiting) %>%
  summarise(injury_vs_vomiting = round(sum(clinically.important.brain.injury == 1)/n(), 2) * 100)

head %>%
  ggplot(aes(x=vomiting,fill=clinically.important.brain.injury)) +
  geom_histogram(stat = "count") +
  xlab("vomiting") +
  labs(title = "vomiting") +
  geom_text(aes(x=1,y=10),label=paste(percent[1,2],"% having injury")) +
  geom_text(aes(x=2,y=10),label=paste(percent[2,2],"% having injury")) +
  ggsave(paste0("figures/histograms/hist_", "vomiting","_vs_brain.injury", ".png"))

percent <- head %>%
  group_by(clinically.important.brain.injury) %>%
  summarise(injury_vs_injury = round(sum(clinically.important.brain.injury == 1)/n(), 2) * 100)

head %>%
  ggplot(aes(x = clinically.important.brain.injury,fill=clinically.important.brain.injury)) +
  geom_histogram(stat = "count") +
  xlab("clinically.important.brain.injury") +
  labs(title = "clinically.important.brain.injury") +
  geom_text(aes(x=1,y=10),label=paste(percent[1,2],"% having injury")) +
  geom_text(aes(x=2,y=10),label=paste(percent[2,2],"% having injury")) +
  ggsave(paste0(
    "figures/histograms/hist_",
    "clinically.important.brain.injury","_vs_brain.injury",
    ".png"
  ))

```




Those percentages will be P(variable X = {0 ; 1} and "individuals who suffered ‘minor’ head injuries" | brain injury)

```{r}

percent <- head %>%
  group_by(clinically.important.brain.injury) %>%
  summarise(age.65_vs_injury = round(sum(age.65 == 1)/n(), 2) * 100)

head %>%
  ggplot(aes(x = clinically.important.brain.injury,fill=age.65)) +
  geom_histogram(stat = "count") +
  xlab("clinically.important.brain.injury") +
  labs(title = "clinically.important.brain.injury") +
  geom_text(aes(x=1,y=10),label=paste(percent[1,2],"% having age.65")) +
  geom_text(aes(x=2,y=100),label=paste(percent[2,2],"% having age.65")) +
  ggsave(paste0(
    "figures/histograms/hist_",
    "clinically.important.brain.injury_vs_","age.65",".png"))

percent <- head %>%
  group_by(clinically.important.brain.injury) %>%
  summarise(amnesia.before_vs_injury = round(sum(amnesia.before == 1)/n(), 2) * 100)

head %>%
  ggplot(aes(x = clinically.important.brain.injury,fill=amnesia.before)) +
  geom_histogram(stat = "count") +
  xlab("clinically.important.brain.injury") +
  labs(title = "clinically.important.brain.injury") +
  geom_text(aes(x=1,y=10),label=paste(percent[1,2],"% having amnesia.before")) +
  geom_text(aes(x=2,y=100),label=paste(percent[2,2],"% having amnesia.before")) +
  ggsave(paste0(
    "figures/histograms/hist_",
    "clinically.important.brain.injury_vs_","amnesia.before",".png"))

percent <- head %>%
  group_by(clinically.important.brain.injury) %>%
  summarise(basal.skull.fracture_vs_injury = round(sum(basal.skull.fracture == 1)/n(), 2) * 100)

head %>%
  ggplot(aes(x = clinically.important.brain.injury,fill=basal.skull.fracture)) +
  geom_histogram(stat = "count") +
  xlab("clinically.important.brain.injury") +
  labs(title = "clinically.important.brain.injury") +
  geom_text(aes(x=1,y=10),label=paste(percent[1,2],"% having basal.skull.fracture")) +
  geom_text(aes(x=2,y=100),label=paste(percent[2,2],"% having basal.skull.fracture")) +
  ggsave(paste0(
    "figures/histograms/hist_",
    "clinically.important.brain.injury_vs_","basal.skull.fracture",".png"))

percent <- head %>%
  group_by(clinically.important.brain.injury) %>%
  summarise(GCS.decrease_vs_injury = round(sum(GCS.decrease == 1)/n(), 2) * 100)

head %>%
  ggplot(aes(x = clinically.important.brain.injury,fill=GCS.decrease)) +
  geom_histogram(stat = "count") +
  xlab("clinically.important.brain.injury") +
  labs(title = "clinically.important.brain.injury") +
  geom_text(aes(x=1,y=10),label=paste(percent[1,2],"% having GCS.decrease")) +
  geom_text(aes(x=2,y=100),label=paste(percent[2,2],"% having GCS.decrease")) +
  ggsave(paste0(
    "figures/histograms/hist_",
    "clinically.important.brain.injury_vs_","GCS.decrease",".png"))

percent <- head %>%
  group_by(clinically.important.brain.injury) %>%
  summarise(GCS.13_vs_injury = round(sum(GCS.13 == 1)/n(), 2) * 100)

head %>%
  ggplot(aes(x = clinically.important.brain.injury,fill=GCS.13)) +
  geom_histogram(stat = "count") +
  xlab("clinically.important.brain.injury") +
  labs(title = "clinically.important.brain.injury") +
  geom_text(aes(x=1,y=10),label=paste(percent[1,2],"% having GCS.13")) +
  geom_text(aes(x=2,y=100),label=paste(percent[2,2],"% having GCS.13")) +
  ggsave(paste0(
    "figures/histograms/hist_",
    "clinically.important.brain.injury_vs_","GCS.13",".png"))

percent <- head %>%
  group_by(clinically.important.brain.injury) %>%
  summarise(GCS.15.2hours_vs_injury = round(sum(GCS.15.2hours == 1)/n(), 2) * 100)

head %>%
  ggplot(aes(x = clinically.important.brain.injury,fill=GCS.15.2hours)) +
  geom_histogram(stat = "count") +
  xlab("clinically.important.brain.injury") +
  labs(title = "clinically.important.brain.injury") +
  geom_text(aes(x=1,y=10),label=paste(percent[1,2],"% having GCS.15.2hours")) +
  geom_text(aes(x=2,y=100),label=paste(percent[2,2],"% having GCS.15.2hours")) +
  ggsave(paste0(
    "figures/histograms/hist_",
    "clinically.important.brain.injury_vs_","GCS.15.2hours",".png"))

percent <- head %>%
  group_by(clinically.important.brain.injury) %>%
  summarise(high.risk_vs_injury = round(sum(high.risk == 1)/n(), 2) * 100)

head %>%
  ggplot(aes(x = clinically.important.brain.injury,fill=high.risk)) +
  geom_histogram(stat = "count") +
  xlab("clinically.important.brain.injury") +
  labs(title = "clinically.important.brain.injury") +
  geom_text(aes(x=1,y=10),label=paste(percent[1,2],"% having high.risk")) +
  geom_text(aes(x=2,y=100),label=paste(percent[2,2],"% having high.risk")) +
  ggsave(paste0(
    "figures/histograms/hist_",
    "clinically.important.brain.injury_vs_","high.risk",".png"))

percent <- head %>%
  group_by(clinically.important.brain.injury) %>%
  summarise(loss.of.consciousness_vs_injury = round(sum(loss.of.consciousness == 1)/n(), 2) * 100)

head %>%
  ggplot(aes(x = clinically.important.brain.injury,fill=loss.of.consciousness)) +
  geom_histogram(stat = "count") +
  xlab("clinically.important.brain.injury") +
  labs(title = "clinically.important.brain.injury") +
  geom_text(aes(x=1,y=10),label=paste(percent[1,2],"% having loss.of.consciousness")) +
  geom_text(aes(x=2,y=100),label=paste(percent[2,2],"% having loss.of.consciousness")) +
  ggsave(paste0(
    "figures/histograms/hist_",
    "clinically.important.brain.injury_vs_","loss.of.consciousness",".png"))

percent <- head %>%
  group_by(clinically.important.brain.injury) %>%
  summarise(open.skull.fracture_vs_injury = round(sum(open.skull.fracture == 1)/n(), 2) * 100)

head %>%
  ggplot(aes(x = clinically.important.brain.injury,fill=open.skull.fracture)) +
  geom_histogram(stat = "count") +
  xlab("clinically.important.brain.injury") +
  labs(title = "clinically.important.brain.injury") +
  geom_text(aes(x=1,y=10),label=paste(percent[1,2],"% having open.skull.fracture")) +
  geom_text(aes(x=2,y=100),label=paste(percent[2,2],"% having open.skull.fracture")) +
  ggsave(paste0(
    "figures/histograms/hist_",
    "clinically.important.brain.injury_vs_","open.skull.fracture",".png"))

percent <- head %>%
  group_by(clinically.important.brain.injury) %>%
  summarise(vomiting_vs_injury = round(sum(vomiting == 1)/n(), 2) * 100)

head %>%
  ggplot(aes(x = clinically.important.brain.injury,fill=vomiting)) +
  geom_histogram(stat = "count") +
  xlab("clinically.important.brain.injury") +
  labs(title = "clinically.important.brain.injury") +
  geom_text(aes(x=1,y=10),label=paste(percent[1,2],"% having vomiting")) +
  geom_text(aes(x=2,y=100),label=paste(percent[2,2],"% having vomiting")) +
  ggsave(paste0(
    "figures/histograms/hist_",
    "clinically.important.brain.injury_vs_","vomiting",".png"))

```


Now, we know:
P(injury | X AND "individuals who suffered ‘minor’ head injuries") and P(X AND "individuals who suffered ‘minor’ head injuries" | injury)
We can deduce:
P(injury) = P(injury | X AND ...) * P(X) / P(X | injury AND ...)

BUT, we will be more precise if we could have it directly from our tutor.

We are asked:
P(injury | X) = P(X|injury) * P(injury) / ( P(X|injury) * P(injury) +  P(X|no injury) * P(no injury) )
Which is the perfect setup for naive Bayes algorithms.

QUESTIONS:
-What percentage of the population is affected by any acute brain finding revealed on CT?
